Scheeper's Meager-NWD Game and the Menger Game

### 2014-05-28 phd/dissertation/chapter3.tex
revisions per meeting with G

(TODO: Any reason for the ``W''?)

Gruenhage defined this game in his doctoral dissertation to define a class
of spaces generalizing first-countability. \cite{MR0413049}

\begin{defn}
  The spaces $X$ for which $\pl O \win \congamehard{X}{x}$ for all $x\in X$ are
  called \term{$W$-spaces}.
\end{defn}

@@

\begin{prop}
  $X$ is first countable
    if and only if
  $\pl O \prewin \congamehard{X}{x}$ for all $x\in X$.
\end{prop}

@@

  If $X$ is not first countable at some $x$, let $\sigma$ be a
  predetermined strategy for $\pl O$ in $\congamehard{X}{x}$. There exists
  an open neighborhood $U$ of $x$ which does not contain any $\sigma(n)$
  (otherwise $\{\sigma(n):n<\omega\}$ would be a countable base at $x$).
  Let $x_n$ be an element of $\sigma(n)\setminus U$ for all $n<\omega$.
  Then $\<x_0,x_1,\dots\>$ is a winning counter-attack to $\sigma$ for $\pl P$,
  so $\pl O$ lacks a winning predetermined strategy.
\end{proof}

@@

Put another way, $\tau(n)=\bigcap_{m\leq n}\sigma(m)$ in the predetermined
case, and
$\tau(\<x_0,\dots,x_{n-1}\>)=\bigcap_{m\leq n}\sigma(\<x_0,\dots,x_{m-1}\>)$
in the perfect information case.
The original proof would have been invalid if $\lambda$ was required to be, say,
the tactical fog-of-war $\nu_1$, since the value of $\pl O$'s own second move
$\sigma\circ\nu_1(\<x_0\>)=\sigma(\<x_0\>)$
could not be determined from the information she has during round
$2$: $\nu_1(\<x_0,x_1\>)=\<x_1\>$.

>>>>

The ``W'' in the name merely refers to $\pl O$'s goal: to ``win'' the game.
Gruenhage defined this game in his doctoral dissertation to define a class
of spaces generalizing first-countability. \cite{MR0413049}

\begin{defn}
  The spaces $X$ for which $\pl O \win \congame{X}{x}$ for all $x\in X$ are
  called \term{$W$-spaces}.
\end{defn}

@@

\begin{prop}
  $X$ is first countable
    if and only if
  $\pl O \prewin \congame{X}{x}$ for all $x\in X$.
\end{prop}

@@

  If $X$ is not first countable at some $x$, let $\sigma$ be a
  predetermined strategy for $\pl O$ in $\congamehard{X}{x}$. There exists
  an open neighborhood $U$ of $x$ which does not contain any 
  $\bigcap_{m\leq n}\sigma(m)$ (otherwise 
  $\{\bigcap_{m\leq n}\sigma(m):n<\omega\}$ would be a countable base at $x$).
  Let $x_n$ be an element of $\bigcap_{m\leq n}\sigma(m)\setminus U$ for all 
  $n<\omega$. Then $\<x_0,x_1,\dots\>$ is a winning counter-attack to $\sigma$ 
  for $\pl P$, so $\pl O$ lacks a winning predetermined strategy.
\end{proof}

@@

Put more simply, $\tau(n)=\bigcap_{m\leq n}\sigma(m)$ in the predetermined
case, and
$\tau(\<x_0,\dots,x_{n-1}\>)=\bigcap_{m\leq n}\sigma(\<x_0,\dots,x_{m-1}\>)$
in the perfect information case.
The original proof would have been invalid if $\lambda$ was required to be, say,
the tactical fog-of-war $\nu_1$, since the value of $\pl O$'s own round $1$ move
$\sigma\circ\nu_1(\<x_0\>)=\sigma(\<x_0\>)$
could not be determined from the information she has during round
$2$: $\nu_1(\<x_0,x_1\>)=\<x_1\>$.
